High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-11-11 discussion.tex
Straggling uncommitted edits

Our results provide more evidence that biologically-inspired models represent a promising
and powerful direction in face recognition research. Individual models from this
class are able to achieve good performance (e.g. around 77\% for \emph{V1-like} models,
84\% for \emph{HT-L3}), and blends of these models achieve more than 88\%
correct performance, beating previously reported state-of-the-art values.

>>>>

Our results provide more evidence that biologically-inspired models represent a promising
and powerful direction in face recognition research. Individual models from this
class are able to achieve good performance (e.g. around 77\% for \emph{V1-like} models,
84\% for \emph{HT-L3}), and blends of these models achieve more than 88\%
correct performance, placing it amongst the best performing systems on this challenge set.
